\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-08 doc/sw-system.tex
Reduced size of figure 12, put to-do note in text #113

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity.png}
\caption{Completeness-estimated purity curves for the \sw system, using
the CFHTLS training set.}
\label{fig:results:sample:CP}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity.png}
\caption{Completeness-estimated purity curves for the \sw system, using
the CFHTLS training set.}
\label{fig:results:sample:CP}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{Chris}{Can you please remake \Fref{fig:results:sample:CP} with a simpler
legend? We can take it as read that Stage 1 was online, Stage 2 was offline,
and the starting values of the matrix elements is 0.5-- and then let's leave
out the different lens types: I think we might just postpone all of that
discussion to \PaperTwo. Last thing: can you make the inset bigger please, to
show us reaching 90\% completeness at 30\% purity? \#113}
